---
title: "Vera Incarceration Trends notes"
author: "Adam Conner-Sax"
output: github_document
---

Data was processed from the Vera incarceration trends data-set (https://github.com/vera-institute/incarceration_trends) and processed (aggregations, filtering, dropping of missing values) byt the author ()

```{r setup, echo = FALSE, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
library(tidyverse)
library(here)
library(hexbin)
library(maps)
library(ggmap)
data(county.fips)
```

Aggregated crime rate and imprisoned per crime by urbanicity: 


```{r urbanicity, echo=FALSE}
urbanicity <- read_csv(here("../../data/","ratesByUrbanicityAndYear.csv"))
ggplot(urbanicity,mapping=aes(color=urbanicity)) + geom_line(mapping=aes(x=year,y=CrimeRate)) + geom_point(mapping=aes(x=year,y=ImprisonedPerCrimeRate)) + facet_grid(rows=vars(urbanicity)) + scale_y_continuous(labels=scales::percent) + labs(x="Year",y="Rate",title="Crime and Prison Admission/Crime by Urbanicity",subtitle="Line is Crime and points are Prison Admission/Crime", caption="Data from Vera Institute of Justice")
```


Combo with poverty/income data

```{r income scatter, echo=TRUE}
trendsWithIncome <- read_csv(here("../../data/", "scatterMergeTest.csv"))
#trends1995 = filter(trendsWithIncome,year==2013)
ggplot(trendsWithIncome,mapping=aes(x=medianHI,y=IncarcerationRate,color=total_pop)) + geom_point() + facet_wrap(~year,ncol=3) + scale_y_continuous(limits=c(NA,0.012), labels = scales::percent)
ggsave("incarcerationRateAndIncome.pdf",width=8,height=11)
```


# From call
Bail reform, CO
have data from open records requests (What data? Just CO?)
clickable map of CO counties
census
cdc
reform policy by location

